---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Magesh Sunder R"
date: "03 Nov 2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application

Using the data provided by GOI Health Ministry, we plot the Locations of the Blood Banks in Tamil Nadu State of India using the Latitudes and Longitudes.

The application is running in (https://mageshsalem.shinyapps.io/my_assignment/)

ui.R, and Server.R Code in my github repository (https://github.com/mageshsalem/Shiny-App)

## Blood Bank Directory (Filtered for one State)

The data used in the app comes from the Government of India Website. 

```{r summary}
library(shiny)

library(dplyr)

library(leaflet)

library(DT)
  
  bb_data <- read.csv("blood-banks_raw_tn.csv", stringsAsFactors = FALSE )
  bb_data <- data.frame(bb_data)
  bb_data$Latitude <-  as.numeric(bb_data$Latitude)
  bb_data$Longitude <-  as.numeric(bb_data$Longitude)
  bb_data=filter(bb_data, Latitude != "NA") # removing NA values
  
```

## Map
the Map displays the Locations of the Blood Banks Visually. if You are not able to view it here kindly click the link below
https://mageshsalem.shinyapps.io/my_assignment/

```{r leaflet}
 # new column for the popup label
  
  bb_data <- mutate(bb_data, cntnt=paste0('<strong>Name: </strong>',Blood.Bank.Name,
                                          '<br><strong>State:</strong> ', City,
                                          '<br><strong>Time:</strong> ', Service.Time,
                                          '<br><strong>Mobile:</strong> ',Mobile,
                                          '<br><strong>HelpLine:</strong> ',Helpline,
                                          '<br><strong>Contact1:</strong> ',Contact.No,
                                          '<br><strong>Email:</strong> ',Email,
                                          '<br><strong>Website:</strong> ',Website)) 

  # create a color paletter for category type in the data file
  
  pal <- colorFactor(pal = c("#1b9e77", "#d95f02", "#7570b3"), domain = c("Charity", "Government", "Private"))

  leafletOutput("bbmap", height=1000)

  # create the leaflet map  
  renderLeaflet({
      leaflet(bb_data) %>% 
      addCircles(lng = ~Longitude, lat = ~Latitude) %>% 
      addTiles() %>%
      addCircleMarkers(data = bb_data, lat =  ~Latitude, lng =~Longitude, 
                       radius = 3, popup = ~as.character(cntnt), 
                       color = ~pal(Category),
                       stroke = FALSE, fillOpacity = 0.8)%>%
      addLegend(pal=pal, values=bb_data$Category,opacity=1, na.label = "Not Available")%>%
      addEasyButton(easyButton(
        icon="fa-crosshairs", title="ME",
        onClick=JS("function(btn, map){ map.locate({setView: true}); }")))
        })
  
```

